Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-04-25 PAPER/main.tex
changed explanation of construction of graph G in section 2, changed captions on figures

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
	\caption{\textcolor{red}{Individual boxes.}}	
	\label{fig:boxknife}
\end{figure}

@@

\begin{itemize}
	\item Figure \ref{fig:partners} shows the graph with the values from the example above
	\item Model each of the values of all pairs in $\mathcal{M}$ as a vertex on a graph $G$
	\item Each vertex is assigned a value from $\mathcal{M}$
	\item Add an extra pair of vertices, dominating vertices, that are assigned values equal to $\tau$
	\item The values in $\mathcal{M}$, and thus the vertices on the graph, are arranged in pairs.
	\item This is represented on the graph by adding a set of ``blue'' edge, $B$, that are a perfect matching of all vertices on the graph
	\item Under such a matching, each vertex (each value in $\mathcal{M}$) has a partner that represents the other value in the pair.
	\item Then, we add to $G$ another set of ``red'' edges, $R$, that consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arrange alongside one another
	\item That is, for two distinct vertices, EQUATION, provided $p(v_i) \neq v_j$ i.e. not partners
	\item Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
	\item $G$ has $2n + 2$ vertices, edge sets $B$ and $R$ such that $B \cap R = \emptyset$
	\item $B = |n+1|$
	\item Dominating vertices are partners
	\item Dominating vertices will be removed at end, are not part of final solution
	\item Vertex set $V = \{v_1,...,v_{2n+2}\}$
	\item Each vertex assigned value from $\mathcal{M}$ s.t. $V-1 \leq ... \leq v_{2n+2}$
\end{itemize}

Let $\mathcal{M}$ be an instance of the COP of cardinality $n$ as described in Definition \ref{defn:cop}. Then, a graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ... \leq v_{2n+2}$. Note that there are two extra ``dominating'' vertices, $v_{2n+1}$ and $v_{2n+2}$, which have values equivalent to $\tau$. In $\mathcal{M}$, the values that make up a pair are referred to as ``partners''. Thus, let $p: V \to V$ be a bijective function that associates each vertex $v_i \in V$ on $G$ with its partner, $v_j = p(v_i)$. $G$ comprises two distinct edge sets: $B$, which contains edges between vertices that are partners, and $R$, which consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arranged alongside one another. That is, for two distinct vertices $v_i, v_j$,

\begin{equation}
	\label{eqn:jointsum}
	v_i + v_j \geq \tau,
\end{equation}

provided $p(v_i) \neq v_j$. Hence, $G=(V, B \cup R)$ is an undirected graph with $2n + 2$ vertices and edge sets $B$ and $R$, such that $B \cap R = \emptyset$. Observe that $B$ is also a perfect matching, with $|B|= n+1$.

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{\textcolor{red}{partners.}}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{\textcolor{red}{threshold.}}	
	\label{fig:threshold}
\end{subfigure}
\caption{$v_1 = 1, v_2 = 1, v_3 = 2, v_4 = 2, v_5 = 3, v_6 = 3, v_7 = 4, v_8 = 4, v_9 = 4, v_{10} = 5, v_{11} = 6, v_{12} = 7, v_{13} = 7, v_{14} = 7$}
\end{figure}

@@

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{\textcolor{red}{matching.}}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{\textcolor{red}{mps}}	
		\label{fig:mps}
	\end{subfigure}
	\caption{main caption}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$. $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.

>>>>

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
	\caption{Width and score widths on an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously}	
	\label{fig:boxknife}
\end{figure}

@@

% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..

Let $\mathcal{M}$ be an instance of the COP of cardinality $n$. We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order. A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$. These dominating vertices aid the solution process, and are removed at the end. Thus, the graph $G$ has $2n+2$ vertices.

The values in $\mathcal{M}$, and thus the vertices on $G$, are arranged in pairs. This is represented on $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e. whose values make up a pair in $\mathcal{M}$. It can be seen that $B$ is a perfect matching, with $|B|= n+1$.

Now, we add to $G$ a set of ``red'' edges, $R$, that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners. This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.

Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$, such that $B \cap R = \emptyset$. Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.

\begin{figure}	
\centering
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/partners}
	\caption{$G = (V, B)$}	
	\label{fig:partners}
\end{subfigure} \hspace{40pt}
\begin{subfigure}[h]{0.45\textwidth}
	\includestandalone[width=\textwidth]{figures/threshold}
	\caption{$G=(V, B \cup R)$}	
	\label{fig:threshold}
\end{subfigure}
\caption{Example construction of $G$ using instance $\mathcal{M}$ from the example above.}
\label{fig:partners/threshold}
\end{figure}

@@

\begin{figure}	
	\centering
	\begin{subfigure}[h]{0.4\textwidth}
		\includestandalone[width=\textwidth]{figures/matching}
		\caption{$G' = (V, B \cup R')$}	
		\label{fig:matching}
	\end{subfigure} \quad
	\begin{subfigure}[h]{0.5\textwidth}
		\includestandalone[width=\textwidth]{figures/mps}
		\caption{$G' =(V, B \cup R')$ planar}	
		\label{fig:mps}
	\end{subfigure}
	\caption{Subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components.}
\end{figure}

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:copsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$. $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.
